---
title: "2014 FEC Data"
author: "Eva Gjekmarkaj"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## FEC 

This is a vignette on how to use the FEC package and conduct analysis for questions such as contributions by individuals/special interests for any given election year. Below I will use the 2014 data to address the following questions:
  
  1. How much money did each State raise?

  2. How much money in aggregate did both parties raise in the 2014 midterm election?
  
  3. How much money was contributed from people to pacs for each committee?

## Connect to a local or remote database 

```{r message=FALSE}
library(fec)
db <- src_mysql_cnf(dbname = "fec", host = "127.0.0.1")
fec <- etl("fec", db = db, dir = "~/dumps/fec")
fec
```


## ETL

  - Doing it all at once
```{r message=FALSE, eval=FALSE, warning=FALSE}
fec %>%
  etl_create(years = 2012)
```

- Note: For more information on [how the ETL Framework works](https://github.com/beanumber/etl)

### How much money did the residents of each state contribute?

```{r, eval=FALSE}
fec %>%
  tbl("individuals") %>%
  group_by(state) %>%
  summarise(Total = sum(transaction_amt)) %>%
  arrange(desc(Total))
```

- Note: There were an additional 8 classifications under the 'state' column. 

### How much money in aggregate did both parties raise the 2014 midterm election?

```{r, eval=FALSE}
committees <- fec %>% tbl("committees")
individuals <- fec %>% tbl("individuals")
Full_Table <- dplyr::full_join(committees, individuals, by = "cmte_id")
amtRaised <- Full_Table %>%
  select(cmte_party_affiliation, transaction_amt) %>%
  group_by(cmte_party_affiliation) %>%
  summarise(Total = sum(transaction_amt)) %>%
  filter(cmte_party_affiliation %in% c("REP", "DEM"))
amtRaised
```

3. How much money was contributed from people to pacs for each committee?

```{r eval=FALSE, results="hide"}
fec %>%
  tbl("people_to_pacs") %>%
  select(party,cmte_name, as.double(total_raised)) %>%
  group_by(party) %>%
  filter(party %in% c("REP", "DEM"))
```

```{r}
## Source:   query [?? x 3]
## Database: mysql  [@Localhost via UNIX socket:/]
## Groups: party

##   party                                              cmte_name total_raised
##   <chr>                                                  <chr>        <dbl>
## 1    DEM            DEMOCRATIC CONGRESSIONAL CAMPAIGN COMMITTEE     72222085
## 2    REP                                                   NRCC     69056167
## 3    DEM               DEMOCRATIC SENATORIAL CAMPAIGN COMMITTEE     58636503
## 4    REP               NATIONAL REPUBLICAN SENATORIAL COMMITTEE     39506955
## 5    DEM                                   PALLONE FOR CONGRESS      3729453
## 6    REP                              BILL CASSIDY FOR CONGRESS      2402917
## 7    DEM                    GEORGIA FEDERAL ELECTIONS COMMITTEE      1339977
## 8    DEM DNC SERVICES CORPORATION/DEMOCRATIC NATIONAL COMMITTEE      1237935
## 9    REP                         MASSACHUSETTS REPUBLICAN PARTY      1123208
## 10   DEM                             STEPHEN LYNCH FOR CONGRESS       745620
# ... with more rows
```

